A template for the \emph{arxiv} style

### 2022-12-02 paper-rmd/paper-papaja-revision.Rmd
added revised paper

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
biblio-style      : "apa"
documentclass     : "apa6"
classoption       : "man"
output:
  papaja::apa6_pdf

header-includes:
  - \usepackage{tikz}
  - \usetikzlibrary{bayesnet}
  - \mathchardef\hyph="2D
---

>>>>

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
biblio-style      : "apa"
documentclass     : "apa6"
classoption       : "man"
output:
  papaja::apa6_word
keep_tex: yes
always_allow_html: true
header-includes:
  - \usepackage{tikz}
  - \usetikzlibrary{bayesnet}
  - \mathchardef\hyph="2D
---
